Learning and Reputation under Monopoly and Duopoly: \\A Competing Bandits Approach

### 2018-08-21 paper/competing_bandits.tex
add footnote

\noindent \textbf{Agents} We suppose that agents are homogenous, myopic, and non-strategic. The utility function for the agents is simply to maximize their reward in the one period in which they are alive. We suppose that agents do not attempt to manipulate the strategy of the firm nor do they take the strategies of the firm into account when choosing between the firms. In our model, each agent uses the average reward of past agents as a proxy for their expected utility. For simplicity, the reputation score, $R_{jt}$ is defined as a sliding window average.
\begin{center}
$R_{jt} = \frac{1}{M} \sum\limits_{i=1}^{M} r_{t_j-i}$
\end{center}

>>>>

\noindent \textbf{Agents} We suppose that agents are homogenous, myopic, and non-strategic. The utility function for the agents is simply to maximize their reward in the one period in which they are alive. We suppose that agents do not attempt to manipulate the strategy of the firm nor do they take the strategies of the firm into account when choosing between the firms. In our model, each agent uses the average reward of past agents as a proxy for their expected utility. For simplicity, the reputation score, $R_{jt}$ is defined as a sliding window average\footnote{Another natural formulation would be to have exponential discounting of the past rewards. We believe that the results should be qualitatively similar to those presented here as in both formulations the more recent past matters more than the distant past.}.
\begin{center}
$R_{jt} = \frac{1}{M} \sum\limits_{i=1}^{M} r_{t_j-i}$
\end{center}
